% !TeX spellcheck = en_US
% !TeX encoding = UTF-8
\chapter*{Acknowledgments}
Many people helped and encouraged me during my Master's studies, and I would like to express my gratitude to all of them. However, there are some people whom I would like to thank individually as their vital contribution helped me get this far.

First, I would like to thank Julian Stier, my thesis advisor, for his constant guidance and encouragement to not only focus on my preliminary research questions but also to explore other possibilities to improve and expand my research interests. He was always quick in providing feedback on my work that allowed me to complete my work promptly.

Secondly, I would like to thank my thesis supervisors, Prof. Dr. Michael Granitzer and Prof. Dr. Harald Kosch. Prof. Granitzer's comments on my initial work helped me expand my thesis work. Their comments during the initial presentation of my work helped me think of original and efficient ways to improve my implementations.

During my studies in Passau, I became friends with people who not only made this city a second home, but they were always there whenever I needed them. One of the important things we all learned from this experience is that a friendship goes beyond any borders.

Finally, but most importantly, I would like to thank my parents and my sister for their continuous support and blessings. They always made sure I get the best education, no matter what the situation is. They have always believed in me, and their combined efforts and sacrifices made it possible for me to continue my Master's education in Germany.